---
title: "Geographical distribution of 2019-nCov as of February 07th 2020"
author: "Myriam Ragni"
date: "8 Februar 2020"
output: html_document
---

## Introduction
The purpose of this assignment is to create a web page using R Markdown that features an interactive map created with Leaflet. I've chosen to represent the propagation of the Coronavirus worldwide, as of February 7th, 2020.  
Data has been extracted from the following source: [Distribution of laboratory confirmed cases of 2019-nCoV worldwide](https://www.ecdc.europa.eu/en/geographical-distribution-2019-ncov-cases).

```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=60), echo = FALSE, eval=TRUE, tidy=TRUE, warning=FALSE, message=FALSE, root.dir="c:/RAGNIMY1/datasciencecoursera/DevelopingDataProducts")
```

```{r Setenv, results="hide"}
rm(list = ls())
Sys.setlocale("LC_TIME", "English")
suppressWarnings(library(leaflet))
suppressWarnings(library(openxlsx))
suppressWarnings(library(dplyr))
suppressWarnings(library(stringr))
```


## Basic Information about the data
```{r PrepareDataset, echo=FALSE}
#### Basic information about the dataset
df <- read.xlsx("./2019-nCov-Case.xlsx",sheet = 1, colNames=TRUE)
df$Latitude <- as.numeric(df$Latitude)
df$Longitude <- as.numeric(df$Longitude)
str(df)
head(df, 10)
```
The dataset used to build the interactive map consists of the number of reported 2019-nCov cases and deaths by region and country.  

## Interactive Map
### Geographical distribution of 2019-nCov as of February 07th 2020

```{r MapLeaflet, fig.height = 8, fig.width = 10, echo=FALSE}
#### Set the threshold for the color of the marker
getColor <- function(df) {
  sapply(df$Cases, function(Cases) {
  if(Cases < 50) {
    "green"
  } else if(Cases < 500) {
    "orange"
  } else {
    "red"
  } })
}

#### Select the 'ios-body' icon from the 'ion' icon library
icons <- awesomeIcons(
  icon = 'ios-body',
  iconColor = 'black',
  library = 'ion',
  markerColor = getColor(df)
)

#### Interactive map with popup text including the country name, the number of reported cases and the number of deaths
nCovMap <- df %>% 
  mutate(Popup = str_c(Country,str_c("Reported Cases: ", Cases), str_c("Deaths: ", Deaths) , sep = "<br/>")) %>%
  leaflet(width = "100%") %>% 
  addProviderTiles("Esri.WorldStreetMap") %>%
  addAwesomeMarkers(lat=~Latitude, lng=~Longitude, icon=icons, popup=~Popup)
nCovMap
```

*Notes*     
* On the map, countries with less than 50 confirmed cases are highlighted in green, those with less than 500 cases in orange and the rest in red.   
* The markers are set on the countries' capital through the cases may not have been reported in that city.   
* Click on a market to get the number of confirmed/reported 2019-nCov cases as well as the number of deaths for a specific country.  

\newpage
## Appendix 
### Preparing the environment
```{r Setup2, ref.label='Setup', echo=TRUE, eval=TRUE}
```

```{r Setenv2, ref.label='Setenv', echo=TRUE, eval=TRUE, results="hide"}
```

### Basic Information about the data
```{r PrepareDataset2, ref.label='PrepareDataset', echo=TRUE, eval=TRUE, results="hide"}
```

### Interactive Map
```{r MapLeaflet2, ref.label='MapLeaflet', echo=TRUE, eval=TRUE, results="hide"}
```